\centerline{\LARGE \bfseries Abstract}
\vspace{0.25in}
\addcontentsline{toc}{chapter}{Abstract}

\medskip
Technology can be a little more disadvantageous than it is advantageous if it is not used by the right
people, in the right time for the right period. In this generation-X, toddlers are way more fluent with
gadgets than many people are. As positive as it may seem on one end, this might kill the creativity
and the colour of social relationship in a kid’s life. Usage of mobile phones and other electronic
gadgets among kids has to be controlled.

\vspace{0.25in}

In an attempt to solve this problem statement this application called “Parent-Pal“ is
developed. This application will provide information of various apps usage in a child’s gadget to the
parent/guardian. The application gets the information of the battery used on different applications
from the phone and with that information, calculates the time spent on each application. This is how
the application works on the child’s end. This information is taken into the database and is stored
there. This data is sent to the parent end of the application for the parent to monitor the usage of
the different applications on the child’s phone. This can also be used in offices to help supervisors in
monitoring the usage of the phone provided by the office to its employees. This application attempts
to give us the control over the technology that we invented. The parent or the manager can hide
this application from the child/employee on their phone. 

\vspace{0.25in}

This application will be built on React-Native using JavaScript. As it is built on React-Native,
this app will be a cross-platform application i.e. it can be used on both android and iOS devices.

\vspace{0.5in}
\begin{flushleft}
\noindent Tools used:\\
React-native\\
Android Studio\\
Firebase\\
Sublime text (text editor)\\
\end{flushleft}
\begin{flushright}
\noindent Submitted by: \\
\noindent Divyanshu(160116737122)\\
\noindent Don Richardson(160115737095)\\
\end{flushright}

\vfill
\newpage